Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-29 main-disk-model.tex

Furthermore, we place ourselves in a context where we do not have perfect knowledge
of the task parameters ($w_u$ and $m_u$) before the tasks start their execution,
but only estimates~\cite{rahman2013,GARG2015256}.  
%. \AB{Add motivation: related work with variable task durations for instance...}
Hence, scheduling decisions are made on these estimated parameters, and
may be reconsidered at runtime when a task starts its execution and we know its exact parameters.

    \subsection{Execution environment}
    \label{sec.mod.plat}
\skug{changes here}
The goal is to execute the workflow on a heterogeneous system, denoted as $\cluster$, which
consists of $k$ processors $p_1, \dots, p_k$.
Each processor $p_j$ ($1 \leq j \leq k$) has an individual memory of size $M_j$ and a speed~$s_j$.
All processors have access to a common disk space of unlimited size, but of much slower speed.
All communications happen over the disk - after one processor has finished writing data there, another one can read
it into its individual memory.
We can decide to evict some data from the individual memory onto the disk to free space in the individual memory.
This data can later be read back into memory of the same or any other processpr at any time.
\skug {check this statement: If data has been written on disk, it is removed from the local memory (no two copies can be kept at the same time).}

>>>>

Furthermore, we place ourselves in a context where we do not have perfect knowledge
of the task parameters ($w_u$ and $m_u$) before the tasks start their execution,
but only estimates~\cite{rahman2013,GARG2015256}.  
%. \AB{Add motivation: related work with variable task durations for instance...}
Hence, scheduling decisions are made on these estimated parameters, and
may be reconsidered at runtime when a task starts its execution and we know its exact parameters.
\AB{Variability only on $w_u$ for now}

    \subsection{Execution environment}
    \label{sec.mod.plat}
\skug{changes here}
The goal is to execute the workflow on a heterogeneous system, denoted as $\cluster$, which
consists of $k$ processors $p_1, \dots, p_k$.
Each processor $p_u$ ($1 \leq u \leq k$) has an individual memory of size $M_u$ and a speed~$s_u$.
All processors have access to a shared disk of unlimited size, where they can write
and read data: Processor~$p_u$ has a bandwidth $\bw_u$ (resp. $\br_u$) to write  (resp. read),
and hence it takes a time $\frac{c_{u,v}}{bw_u}$ to write the data produced for~$p_v$, 
if this data is evicted from memory.

%, but of much slower speed.
All communications happen over the disk - after one processor has finished writing data there, another one can read
it into its individual memory.
We can decide to evict some data from the individual memory onto the disk to free space in the individual memory.
This data can later be read back into memory of the same or any other processpr at any time.
\skug {check this statement: If data has been written on disk, it is removed from the local memory (no two copies can be kept at the same time).}
